Estimating Trending Topics on Twitter with Small Subsets of the Total Data

### 2015-01-12 521_project_paper.tex
changed parameters of the history data struct

>>>>

Things to add:
abstract
clear definition of problem and motivation 
adapt proposal -> introduction stuff
background work: cm-sketch, hokusai (algorithm), specific twitter trending work: ? 
http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=6137387&tag=1 
(this is the closest we could find)
(to the best of our knowledge, this work has not been done before)

how did we approach it 
overview

data structures

algorithms
clean up algorithm section
- make sure changes in implementation are reflected in algorithm

justification

results

naive algorithm serves as comparison
description of naive

the results

future work

references
